\texttt{yacoub}: a Python package for Simulating Generalized Fading Channels

### 2018-03-07 paper/yacoub.tex
add stuff
push stuff

\author{\IEEEauthorblockN{Jos\'e~V.~de~M.~Cardoso,~Paulo~R.~Lins~Jr,~Wamberto~J.~L.~Queiroz,
                          ~and~Marcelo~S.~Alencar,~\textit{IEEE Senior Member}}
\IEEEauthorblockA{Universidade Federal de Campina Grande\\
Campina Grande, Para\'iba, Brazil\\
\{josevinicius,paulo,wamberto,malencar\}@iecom.org.br\\}
}

@@

\begin{abstract}
    We present a well tested Python-based library for simulating and computing
    generalized fading channels, named \texttt{yacoub}. We describe the
    applicability of \texttt{yacoub} using examples in recent communications
    system, namely: cooperative spectrum sensing, bit error rate computation
    in generalized fading, and free space optics. The development of \texttt{yacoub}
    open source and its code is avaliable at \texttt{http://github.com/mirca/yacoub}.
\end{abstract}

@@

\section{Examples}
\subsection{Signal detection}
\subsection{Free Space Optics}
\subsection{BER in $\alpha-\mu$ Fading}

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,aps2016_regular.bib}

>>>>

\author{\IEEEauthorblockN{Jos\'e~V.~de~M.~Cardoso,~Paulo~R.~Lins~Jr,
                          ~and~Marcelo~S.~Alencar,~\textit{IEEE Senior Member}}
\IEEEauthorblockA{Universidade Federal de Campina Grande\\
Instituto Federal de Educa\c c\~ao, Ciencia, e Tecnologia da Para\'iba
Campina Grande, Para\'iba, Brazil\\
\{josevinicius,paulo,malencar\}@iecom.org.br\\}
}

@@

\begin{abstract}
    We present a well tested Python-based library for simulating and computing
    generalized fading channels, named \texttt{yacoub}. We describe the
    applicability of \texttt{yacoub} using examples in recent communications
    systems challenges, namely: cooperative spectrum sensing, bit error rate computation
    in generalized fading, and free space optics. The development of \texttt{yacoub}
    open source and its code is avaliable at \texttt{http://github.com/mirca/yacoub}.
\end{abstract}

@@

\section{Examples}
\subsection{Signal detection and estimation}
\subsection{Free Space Optics}
\subsection{BER in $\alpha-\mu$ Fading}

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv, yacoub.bib}
